### 2024-01-05 paper/si_sections/2_ml.tex
get tables for cleaning up

Supplementary Figure 19 | Pairwise Plot of Adsorption Energy and Key Descriptors. This chart displays the pairwise relationships between CO adsorption energy and its four most correlated descriptors–d-band center (spin-up) δεd↑, lattice parameter γ, vacuum level Evac, and electronegativity on the Allen scale XAllen –as identified by Kendall rank correlation analysis. Data from all six substrates investigated in this study are incorporated.

Supplementary Table 15
Notations for elementary descriptors and electronic descriptors
Elementary Descriptors	Electronic Descriptors
R	atomic radius	α, β, γ	lattice parameters
Eea	electron affinity	ΦDFT	DFT calculated work function
Φ	work function	Evac	vacuum level
XAllen, ΧP, ΧRevP	electronegativity in Allen, Pauling and revised Pauling scales	Eg, Eg↑, Eg↓	average, spin-up and spin-down band gaps
Ar	relative atomic mass	ed	number of d-electrons
Ei	ionisation energy	δεd↑	d-band centre (spin-up)
G	group number	Wd	d-band width
P	period number	eBader	Bader charge
V	number of valence electrons

@@

Supplementary Table 16
The hyperparameter searching space
Hyperparameter	Search space	Description
learningRate	[10-4, 10-2], logscale	Learning rate of Adam optimiser
dropoutRate	[0, 1]	Dropout rate
root_fc0	128, 256, 512	Output dimensionality of 1st fully connected layer in root
root_fc1	256, 512, 1024, 2048	Output dimensionality of 2nd fully connected layer in root
root_act	"tanh", "relu", "sigmoid"	Activation function of fully connected layers in root
kernelSize	[2, 32]	Width of convolution window
numFilters	[8, 64]	Number of filters in the convolution
numConvLayers	[1, 16]	Number of convolution layers
numConvBlocks	[1, 16]	Number of convolution blocks
br_fc0	16, 32, 64, 128, 256, 512	Output dimensionality of 1st fully connected layer in branch
br_fc1	8, 16, 32, 64, 128, 256	Output dimensionality of 2nd fully connected layer in branch
br_act	"tanh", "relu", "sigmoid"	Activation function of fully connected layers in branch

Supplementary Table 17
Optimal hyperparameters identified with Hyperband algorithm
Hyperparameter	Optimal value	Description
learningRate	10-3	Learning rate of Adam optimiser
dropoutRate	0.3	Dropout rate
root_fc0	256	Output dimensionality of 1st fully connected layer in root
root_fc1	512	Output dimensionality of 2nd fully connected layer in root
root_act	“relu”	Activation function of fully connected layers in root
kernelSize	10	Width of convolution window
numFilters	17	Number of filters in the convolution
numConvLayers	3	Number of convolution layers
numConvBlocks	1	Number of convolution blocks
br_fc0	256	Output dimensionality of 1st fully connected layer in branch
br_fc1	128	Output dimensionality of 2nd fully connected layer in branch
br_act	“tanh”	Activation function of fully connected layers in branch

Supplementary Table 18
Prediction mean absolute errors of the CNN model
Adsorbate	Original dataset (eV)	Augmented dataset (eV)
CO2	0.0447	0.0336
COOH	0.0436	0.0581
CO	0.0402	0.0402
CHO	0.0614	0.0778
CH2O	0.0553	0.0632
OCH3	0.0605	0.0636
O	0.1135	0.1081
OH	0.0547	0.0602
H	0.0703	0.0646
Note. The same CNN model, trained on the augmented dataset, was used for all predictions. The term “Original dataset” refers to evaluations conducted on the original dataset without any augmented data; it does not imply the use of a different CNN model trained solely on the original dataset. Similarly, “Augmented dataset” refers to evaluations on the dataset with both original data and augment data, not a distinct model.

@@

Supplementary Figure 22 | Occlusion Experiment with a masker width of “1”. This figure shows an occlusion experiment on the Ge atom in the initial state of CO adsorption on Ge@g-C3N4.

Supplementary Figure 23 | Occlusion Experiment with a masker width of “3”. This figure shows an occlusion experiment on the Ge atom in the initial state of CO adsorption on Ge@g-C3N4.

Supplementary Figure 24 | Occlusion Experiment with a masker width of “5”. This figure shows an occlusion experiment on the Ge atom in the initial state of CO adsorption on Ge@g-C3N4.

Supplementary Figure 25 | Occlusion Experiment with a masker width of “11”. This figure shows an occlusion experiment on the Ge atom in the initial state of CO adsorption on Ge@g-C3N4.

Supplementary Figure 26 | Occlusion Experiment with a masker width of “21”. This figure shows an occlusion experiment on the Ge atom in the initial state of CO adsorption on Ge@g-C3N4.

Supplementary Figure 27 | Occlusion Experiment with a masker width of “31”. This figure shows an occlusion experiment on the Ge atom in the initial state of CO adsorption on Ge@g-C3N4.

Supplementary Figure 28 | Occlusion Experiment with a masker width of “41”. This figure shows an occlusion experiment on the Ge atom in the initial state of CO adsorption on Ge@g-C3N4.

Supplementary Figure 29 | Occlusion Experiment with a masker width of “51”. This figure shows an occlusion experiment on the Ge atom in the initial state of CO adsorption on Ge@g-C3N4.

@@

Supplementary Figure 31 | Shifting Experiment on p orbital. Effect of orbital shifting on CO adsorption energy, predicted by the CNN model, for single metal atom catalysts supported on g-C3N4. The perturbations caused by shifting of entire p orbital are presented. The shifting step size corresponds to the energy resolution of the eDOS, set at 0.005 eV in this study. A positive eDOS shift indicates a shift towards higher energy levels, and vice versa.

>>>>

Supplementary Figure 19 | Pairwise Plot of Adsorption Energy and Key Descriptors. This chart displays the pairwise relationships between CO adsorption energy and its four most correlated descriptors-d-band center (spin-up) δεd↑, lattice parameter γ, vacuum level Evac, and electronegativity on the Allen scale XAllen -as identified by Kendall rank correlation analysis. Data from all six substrates investigated in this study are incorporated.

% Supplementary Table 15
\begin{table}[h]
    \centering
    \begin{tabular}{lr}
      \hline
      Elementary Descriptors	Electronic Descriptors
      \hline
      R	atomic radius	α, β, γ	lattice parameters
      Eea	electron affinity	ΦDFT	DFT calculated work function
      Φ	work function	Evac	vacuum level
      XAllen, ΧP, ΧRevP	electronegativity in Allen, Pauling and revised Pauling scales	Eg, Eg↑, Eg↓	average, spin-up and spin-down band gaps
      Ar	relative atomic mass	ed	number of d-electrons
      Ei	ionisation energy	δεd↑	d-band centre (spin-up)
      G	group number	Wd	d-band width
      P	period number	eBader	Bader charge
      V	number of valence electrons
      \hline
    \end{tabular}
    \caption{Notations for elementary descriptors and electronic descriptors}
    \label{si_table15}
\end{table}

@@

% Supplementary Table 16
\begin{table}[h]
    \centering
    \begin{tabular}{lr}
      \hline
      Hyperparameter	Search space	Description
      \hline
      learningRate	[10-4, 10-2], logscale	Learning rate of Adam optimiser
      dropoutRate	[0, 1]	Dropout rate
      root_fc0	128, 256, 512	Output dimensionality of 1st fully connected layer in root
      root_fc1	256, 512, 1024, 2048	Output dimensionality of 2nd fully connected layer in root
      root_act	"tanh", "relu", "sigmoid"	Activation function of fully connected layers in root
      kernelSize	[2, 32]	Width of convolution window
      numFilters	[8, 64]	Number of filters in the convolution
      numConvLayers	[1, 16]	Number of convolution layers
      numConvBlocks	[1, 16]	Number of convolution blocks
      br_fc0	16, 32, 64, 128, 256, 512	Output dimensionality of 1st fully connected layer in branch
      br_fc1	8, 16, 32, 64, 128, 256	Output dimensionality of 2nd fully connected layer in branch
      br_act	"tanh", "relu", "sigmoid"	Activation function of fully connected layers in branch
      \hline
    \end{tabular}
    \caption{The hyperparameter searching space}
    \label{si_table16}
\end{table}

% Supplementary Table 17
\begin{table}[h]
    \centering
    \begin{tabular}{lr}
      \hline
      Hyperparameter	Optimal value	Description
      \hline
      learningRate	10-3	Learning rate of Adam optimiser
      dropoutRate	0.3	Dropout rate
      root_fc0	256	Output dimensionality of 1st fully connected layer in root
      root_fc1	512	Output dimensionality of 2nd fully connected layer in root
      root_act	“relu”	Activation function of fully connected layers in root
      kernelSize	10	Width of convolution window
      numFilters	17	Number of filters in the convolution
      numConvLayers	3	Number of convolution layers
      numConvBlocks	1	Number of convolution blocks
      br_fc0	256	Output dimensionality of 1st fully connected layer in branch
      br_fc1	128	Output dimensionality of 2nd fully connected layer in branch
      br_act	“tanh”	Activation function of fully connected layers in branch
      \hline
    \end{tabular}
    \caption{Optimal hyperparameters identified with Hyperband algorithm}
    \label{si_table17}
\end{table}

% Supplementary Table 18
\begin{table}[h]
    \centering
    \begin{tabular}{lr}
      \hline
      Adsorbate	Original dataset (eV)	Augmented dataset (eV)
      \hline
      CO2	0.0447	0.0336
      COOH	0.0436	0.0581
      CO	0.0402	0.0402
      CHO	0.0614	0.0778
      CH2O	0.0553	0.0632
      OCH3	0.0605	0.0636
      O	0.1135	0.1081
      OH	0.0547	0.0602
      H	0.0703	0.0646
      \hline
    \end{tabular}
    \caption{Prediction mean absolute errors of the CNN model}
    \label{si_table18}
\end{table}
Note. The same CNN model, trained on the augmented dataset, was used for all predictions. The term “Original dataset” refers to evaluations conducted on the original dataset without any augmented data; it does not imply the use of a different CNN model trained solely on the original dataset. Similarly, “Augmented dataset” refers to evaluations on the dataset with both original data and augment data, not a distinct model.

@@

Supplementary Figure 22 | Occlusion Experiment with a masker width of “1”. This figure shows an occlusion experiment on the Ge atom in the initial state of CO adsorption on Ge@g-C$_3$N$_4$.

Supplementary Figure 23 | Occlusion Experiment with a masker width of “3”. This figure shows an occlusion experiment on the Ge atom in the initial state of CO adsorption on Ge@g-C$_3$N$_4$.

Supplementary Figure 24 | Occlusion Experiment with a masker width of “5”. This figure shows an occlusion experiment on the Ge atom in the initial state of CO adsorption on Ge@g-C$_3$N$_4$.

Supplementary Figure 25 | Occlusion Experiment with a masker width of “11”. This figure shows an occlusion experiment on the Ge atom in the initial state of CO adsorption on Ge@g-C$_3$N$_4$.

Supplementary Figure 26 | Occlusion Experiment with a masker width of “21”. This figure shows an occlusion experiment on the Ge atom in the initial state of CO adsorption on Ge@g-C$_3$N$_4$.

Supplementary Figure 27 | Occlusion Experiment with a masker width of “31”. This figure shows an occlusion experiment on the Ge atom in the initial state of CO adsorption on Ge@g-C$_3$N$_4$.

Supplementary Figure 28 | Occlusion Experiment with a masker width of “41”. This figure shows an occlusion experiment on the Ge atom in the initial state of CO adsorption on Ge@g-C$_3$N$_4$.

Supplementary Figure 29 | Occlusion Experiment with a masker width of “51”. This figure shows an occlusion experiment on the Ge atom in the initial state of CO adsorption on Ge@g-C$_3$N$_4$.

@@

Supplementary Figure 31 | Shifting Experiment on p orbital. Effect of orbital shifting on CO adsorption energy, predicted by the CNN model, for single metal atom catalysts supported on g-C$_3$N$_4$. The perturbations caused by shifting of entire p orbital are presented. The shifting step size corresponds to the energy resolution of the eDOS, set at 0.005 eV in this study. A positive eDOS shift indicates a shift towards higher energy levels, and vice versa.

### 2024-01-05 paper/si_sections/3_others.tex
get tables for cleaning up

The hyperparameter optimization for the proposed CNN model was performed using NVIDIA® V100 Tensor Core GPUs, courtesy of the Australian National Computational Infrastructure's (NCI) HPC Gadi system. The HyperBand algorithm \cite{li2018hyperband}, as implemented in KerasTuner \cite{omalley2019kerastuner} , facilitated the tuning process.

Supplementary Table 19
Core packages in deep learning environment
Name	Version	Build	Channel
conda	4.13.0	py39h06a4308_0	anaconda
cuda-nvcc	11.8.89	0	nvidia
cuda-toolkit	11.8.0	0	nvidia
cudatoolkit	11.6.0	habf752d_9	nvidia
ipykernel	6.9.1	py39h06a4308_0	anaconda
ipython	7.34.0	pypi_0	pypi
jupyter_client	7.2.2	py39h06a4308_0	anaconda
jupyterlab	3.4.4	py39h06a4308_0	anaconda
keras	2.9.0	pypi_0	pypi
keras-preprocessing	1.1.2	pypi_0	pypi
keras-tuner	1.3.5		pypi
matplotlib	3.5.1	py39h06a4308_1	anaconda
numpy	1.22.4	pypi_0	pypi
pandas	1.3.4	py39h8c16a72_0	anaconda
python	3.9.12	h12debd9_1	anaconda
scikit-learn	1.1.1	py39h6a678d5_0	anaconda
scipy	1.8.1	py39hddc5342_3	conda-forge
tensorboard	2.9.1	pypi_0	pypi
tensorflow	2.9.3	pypi_0	pypi
tensorflow-gpu	2.9.3	pypi_0	pypi
xlrd	2.0.1	pyhd3eb1b0_0	anaconda
yaml	0.2.5	h7b6447c_0	anaconda
Note. The complete list of packages is provided along with the source code.

@@

Supplementary Table 20
Core packages in data analysis and visualization environment
Name	Version	Build	Channel
bokeh	3.2.2	pypi_0	pypi
colorcet	3.0.1	pypi_0	pypi
heatmapz	0.0.4	pypi_0	pypi
keras	2.13.1	pypi_0	pypi
keras-tuner	1.3.5	pypi_0	pypi
matplotlib	3.7.2	pypi_0	pypi
numpy	1.24.3	pypi_0	pypi
pandas	2.0.3	pypi_0	pypi
python	3.11.4	hb885b13_0
pyyaml	6.0.1	pypi_0	pypi
scikit-learn	1.3.0	pypi_0	pypi
scipy	1.11.1	pypi_0	pypi
seaborn	0.12.2	pypi_0	pypi
tensorboard	2.13.0	pypi_0	pypi
tensorflow	2.13.0	pypi_0	pypi
tensorflow-macos	2.13.0	pypi_0	pypi
Note. The complete list of packages is provided along with the source code.

>>>>

The hyperparameter optimization for the proposed CNN model was performed using NVIDIA$^{\textregistered}$ (TODO:) V100 Tensor Core GPUs, courtesy of the Australian National Computational Infrastructure's (NCI) HPC Gadi system. The HyperBand algorithm \cite{li2018hyperband}, as implemented in KerasTuner \cite{omalley2019kerastuner} , facilitated the tuning process.

% Supplementary Table 19
\begin{table}[h]
    \centering
    \begin{tabular}{lr}
      \hline
      Name	Version	Build	Channel
      \hline
      conda	4.13.0	py39h06a4308_0	anaconda
      cuda-nvcc	11.8.89	0	nvidia
      cuda-toolkit	11.8.0	0	nvidia
      cudatoolkit	11.6.0	habf752d_9	nvidia
      ipykernel	6.9.1	py39h06a4308_0	anaconda
      ipython	7.34.0	pypi_0	pypi
      jupyter_client	7.2.2	py39h06a4308_0	anaconda
      jupyterlab	3.4.4	py39h06a4308_0	anaconda
      keras	2.9.0	pypi_0	pypi
      keras-preprocessing	1.1.2	pypi_0	pypi
      keras-tuner	1.3.5		pypi
      matplotlib	3.5.1	py39h06a4308_1	anaconda
      numpy	1.22.4	pypi_0	pypi
      pandas	1.3.4	py39h8c16a72_0	anaconda
      python	3.9.12	h12debd9_1	anaconda
      scikit-learn	1.1.1	py39h6a678d5_0	anaconda
      scipy	1.8.1	py39hddc5342_3	conda-forge
      tensorboard	2.9.1	pypi_0	pypi
      tensorflow	2.9.3	pypi_0	pypi
      tensorflow-gpu	2.9.3	pypi_0	pypi
      xlrd	2.0.1	pyhd3eb1b0_0	anaconda
      yaml	0.2.5	h7b6447c_0	anaconda
      \hline
    \end{tabular}
    \caption{Core packages in deep learning environment}
    \label{si_table19}
\end{table}
Note. The complete list of packages is provided along with the source code.

@@

% Supplementary Table 20
\begin{table}[h]
    \centering
    \begin{tabular}{lr}
      \hline
      Name	Version	Build	Channel
      \hline
      bokeh	3.2.2	pypi_0	pypi
      colorcet	3.0.1	pypi_0	pypi
      heatmapz	0.0.4	pypi_0	pypi
      keras	2.13.1	pypi_0	pypi
      keras-tuner	1.3.5	pypi_0	pypi
      matplotlib	3.7.2	pypi_0	pypi
      numpy	1.24.3	pypi_0	pypi
      pandas	2.0.3	pypi_0	pypi
      python	3.11.4	hb885b13_0
      pyyaml	6.0.1	pypi_0	pypi
      scikit-learn	1.3.0	pypi_0	pypi
      scipy	1.11.1	pypi_0	pypi
      seaborn	0.12.2	pypi_0	pypi
      tensorboard	2.13.0	pypi_0	pypi
      tensorflow	2.13.0	pypi_0	pypi
      tensorflow-macos	2.13.0	pypi_0	pypi
      \hline
    \end{tabular}
    \caption{Core packages in data analysis and visualization environment}
    \label{si_table20}
\end{table}
Note. The complete list of packages is provided along with the source code.
